\documentclass[a4paper,12pt]{article}
\begin{document}
\title{A CONCEPT PAPER ON REASONS FOR STUDENTS' PREFERENCE ON RESIDENCE.}
\author{Kikomeko musa 	Student:215004259 Regno.:15/u/6675/ps} 

\maketitle
\section{Introduction.}
when ever students are admitted to the university they tend to reside from different places and this is more so when ever freshers join campus,or those who have been commuting, decide to look for hostels and halls around Makerere university, they will always ask "which one is better, with good facilities?".
The worry should be no more as we i take you through the best residential place that students have over the years graded as comfort zones.
\newline
\newline
students find it hard to decide where to reside during the course of the education at the university.they proclaim that every residential pLace has its attributed difficulties and benefits:


\textbf{COMMUTING STUDENTS:} 
enjoy not incurring costs for rent and feeding even though they suffer the problem of destruction from home.


\textbf{HOSTEL STUDENTS} enjoy un controlled freedom and facilities that enable us pass For example, a swimming pool, gym, free kitchens on every flow, free Wi-Fi or Internet and so much more.how ever these suffer high costs of rent and feeding together with security loopholes.


\textbf{STUDENTS IN THE HALLS}enjoy company and solidarity,team work and security even though they face a problem of high population within each room.
This has left different conclusion over which option is best and preferred for residence for the university students.
\subsection{Background to the problem.}
Many students more especially freshers find it hard to to decide where to dwell,with their little knowledge about how the university operates so they are burdened to take a decision.


Even continuing students that were once commuting find it hard to locate the different halls they are attached to or even the different hostels they would wish to reside during their time at the university. 
\subsection{Problem Statement.}
the students' ignorance about the benefits and dangers of the different residential places.


The cost benefit relationship for the residential places students have to put in consideration before deciding which residential place to opt for.
\section{Aim and Objectives.}
\subsection{Main Objective.}
 To guide students when selecting their residential places upon admission.
 to find out which hall has most students,their category and their nature of residence for solving problems of such a trend.
 
 Our goal is to help students to find in a fast way of allocating the different hostels and halls.
\newline We try to avoid the time-consuming concept when students are allocating different residential places and minimizing the risk of corn men that exploit the students' ignorance about these places.
\subsection{Specific Objectives.}
\begin{itemize}
\item To avoid the reasons why students reside in different residential place.this is in form of working upon the cited problems within the respective residential places so that they attract more.
\item To find out why students opt for different places and which category of students. this is in form of how a different category of students can be helped out with issues of residence. 
\item To identify the loopholes in the different residential place and how they can be minimized.this is achievable by inquiring individuals why they opted their places of residence in instead of all others
\end{itemize}
\section{Methodology}	
\subsection{interview}
\paragraph{here i reached a good number of students asking them about the reasons as to why they chose their respective places of residence,what problems they face in those places and their suggestions}
\subsection{observation}
\paragraph{i reached different hostels and halls of residence within the university to observe what happens within these places,their sanitation and all related activities in and around them}
\section{REFERENCES}\label{sec:intro}
{	role: {custodian MISH},
	name:  {Miss hawa},
}


{
	role: {custodian OLYMPIA},
	name:  {Miss harriet},
}

{
	role: {chairman NKURUMAH hall},
	name:  {Mr mutyaba},
}
\end{document}
